### 2020-08-08 paper/main.tex
Minor style fixes

\usepackage[
	style=alphabetic
]{biblatex}
\addbibresource{bbl.bib}

@@

\paragraph{Editorial notes}
\begin{itemize}
	\item By solid lines we will mark edges, by dashed lines we will mark nonedges, when significant. Sometimes nonedges will not be marked in order not to clutter the image.
	\todo{Where should we put it?}
	\item A node is $X$-complete in $G$ iff it is adjacent to all nodes in $X$.
	\item Given a path $P$, by $P^*$ we will denote its inside.
\end{itemize}

\TODO{Give some examples why are these interesting, some subclasses, and problems that are solvable for perfect graphs, including recognition and coloring}

Given a graph $G$, its \emph{complement} $\overline{G}$ is a graph with the same vertex set and in which two distinct nodes $u, v$ are connected in $\overline{G}$ iff they are not connected in $G$. For example a clique in a graph becomes an independent set in its complement. A perfect graph theorem, first conjured by Berge in 1961 \cite{CB61} and then proven by \Lovasz in 1972 \cite{LL72} states that a graph is perfect iff its complement graph is also perfect. \todo{Should we give some proof of that here? Maybe based on proof in \cite{GC03}}

@@

Odd holes are not perfect, since their chromatic number is 3 and their largest cliques are of size 2. It is easy to see, that an odd antihole of size $n$ has a chromatic number of $\frac{n+1}{2}$ and largest cliques of size $\frac{n-1}{2}$. It is therefore clear, that if a graph is not Berge it is not perfect. To prove that every Berge graph is perfect is the proper part of the strong perfect graph theorem.

@@

\TODO{Cite the paper and tell this is only a short overview}

@@

\TODO{Main ideas of the algorithm.}
\TODO{First we check all on $G$, then on $\overline{G}$}

\subsubsection{Simple structures}

@@

Most obvious way to find a jewel would be to enumerate all choices of $v_1, \ldots v_5$, check if a choice is correct and if it is try to find a path $P$ as required. This gives us a time of $O(|V|^7)$. We could speed it up to $O(|V|^6)$ with more careful algorithm, but since whole algorithms takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we used this simple algorithm.

@@

\TODO{image?}

@@

\subsubsection{Amenable holes.}

@@

Finding and Using Half-Cleaners.\\

Overview of proof of why algorithm using Half-Cleaners is correct.\\

>>>>

\usepackage[
	style=numeric
]{biblatex}
\addbibresource{bbl.bib}

@@

\paragraph{Definitions and conventions}
	\todo{Where should we put it? Should we put all definitions here, or leave them in text?}
\begin{itemize}
	\item By solid lines we will mark edges, by dashed lines we will mark nonedges, when significant. Sometimes nonedges will not be marked in order not to clutter the image.
	\item A node is $X$-complete in $G$ iff it is adjacent to all nodes in $X$.
	\item Given a path $P$, by $P^*$ we will denote its inside.
\end{itemize}

\TODO{Give some examples why perfect graphs are interesting, some subclasses, and problems that are solvable for perfect graphs, including recognition and coloring}

Given a graph $G$, its \emph{complement} $\overline{G}$ is a graph with the same vertex set and in which two distinct nodes $u, v$ are connected in $\overline{G}$ iff they are not connected in $G$. For example a clique in a graph becomes an independent set in its complement. A perfect graph theorem, first conjured by Berge in 1961~\cite{CB61} and then proven by \Lovasz in 1972~\cite{LL72} states that a graph is perfect iff its complement graph is also perfect. \todo{Should we give some proof of that here? Maybe based on proof in \cite{GC03}}

@@

Odd holes are not perfect, since their chromatic number is 3 and their largest cliques are of size 2. It is also easy to see, that an odd antihole of size $n$ has a chromatic number of $\frac{n+1}{2}$ and largest cliques of size $\frac{n-1}{2}$. It is therefore clear, that if a graph is not Berge it is not perfect. To prove that every Berge graph is perfect is the proper part of the strong perfect graph theorem.

@@

The following is based on the paper by Maria Chudnovsky et al. \citetitle*[]{MC05}. We will not provide full proof of its correctness, but will aim to show the intuition behind the algorithm.

@@

Berge graph recognition algorithm could be divided into two parts: first we check if either $G$ or $\overline{G}$ contain any of a number of simple structures as a induced subgraph (\ref{SimpleStructures}). If they do, we output that graph is not Berge and stop. Else, we check if there is a near-cleaner for a shortest odd hole.(\ref{AmenableHoles}).

\subsubsection{Simple structures}
\label{SimpleStructures}

@@

Most obvious way to find a jewel would be to enumerate all choices of $v_1, \ldots v_5$, check if a choice is correct and if it is try to find a path $P$ as required. This gives us a time of $O(|V|^7)$. We could speed it up to $O(|V|^6)$ with more careful algorithm, but since whole algorithms takes time $O(|V|^9)$ and our testing showed that time it takes to test for jewels is negligible we decided against it.

@@

\TODO{picture?}

@@

\subsubsection{Amenable holes.}
\label{AmenableHoles}

@@

\TODO{Finding and Using Half-Cleaners.}

\TODO{Overview of proof of why algorithm using Half-Cleaners is correct.}
